Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-19 ebayes_rnaseq_heterosis.tex
updated discussion of map estimates

We found MAP estimates for both the independence and covariance models as shown in Table \ref{t:map}. 
% Need MAP estimates table and discussion

>>>>

We found MAP estimates for both the independent and covariance models as shown in Table \ref{t:map}. 
\input{include/map}
The MAP estimates for the hierarchical means, $\eta$, and standard deviations, $\sigma$, are consistent between the the independent and covariance model with, perhaps, a slightly larger mean and smaller standard deviation for the logarithm of the overdispersion parameter, $\log(\psi_g)$ in the covariance model relative to the independent model. In the covariance model, there appears to be high correlation amongst the expression means, $\eta_i$ for $i=1,2,3$, and the expression means are negatively correlated with the (log) overdispersion parameter. The sequencing depth terms, and their variance, are consistent between the two models, with the estimates for the covariance model being consistently 0.02 larger than the independent model, and both indicating that there is about a 25\% increase in counts between the least and most thoroughly sequenced samples.
